Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-08-22 BD_radvel/mn060888mj_rev/kurosawa.tex
Some typos fixed. RK.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@792 25464f21-6099-402c-b30a-640f1d40d38b

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard
HD~140538 \textcolor{red}{(G2.5V)}
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed \'{e}celle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric 
\textcolor{red}{
$\mathrm{RV_{HD\,140538}=}19.17\pm0.40\,\kmps$
}
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.
\textcolor{red}{
  Note that the uncertainty in $\mathrm{RV_{HD\,140538}}$ was computed
  by combining (in quadrature) the uncertainty ($0.4~\kmps$) in the
  heliocentric RV of the template star HD~74497 (G3V) and the
  uncertainty in the relative RV of HD~140538 ($0.02~\kmps$), measured
  by cross correlation with the template star.  Clearly, the former
  dominates in the uncertainty in the value of
  $\mathrm{RV_{HD\,140538}}$ shown above. The uncertainty in the
  heliocentric RV of the template is rather large because it was
  determined from a few photospheric lines.
}

@@

\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
  observed (relative) RV values with a constant (a horizontal
  line). The constant used in the fit is determined from the weighted mean of
  the two RV measurements for each object.  The objects with
  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
  which appear in the right-most bin in the histogram. There
  are four objects which satisfy this condition. 
  \textcolor{red}{The expected distribution (dashed) for RV constant
  objects is also shown for a comparison. The distribution is
  normalized with the total number of objects that have $p<10^{-3}$}.
  The match between the expected distribution and the
  histogram is reasonable \textcolor{red}{(c.f.~Section~\ref{sub:Radial-velocities})},
  indicating that our uncertainty estimates 
  in RV values are also reasonable.  }

@@

Follow-up spectroscopic observations of the binary candidates
presented here are planned in near future. There are only a few RV
variable binary candidates identified in earlier surveys
(\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
As \citet{burgasser:2006} points out most of the current RV and
imaging surveys use samples from magnitude-limited survey, but one
should attempt to use the samples from volume-limited survey in order
to find a correct statistics on binary parameters more straightforwardly,
i.e. without correcting for bias. 
\textcolor{red}{
It is possible that out binary fraction is an overestimate since we
are biased to brighter objects. However the lack of a double-lined
system suggests that a primary-to-secondary luminosity ratio of $\gg 1$
for the RV variables found in this paper. 
}

>>>>

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard
HD~140538 \textcolor{red}{(G2.5V)}
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed \'{e}celle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric 
\textcolor{red}{
$\mathrm{RV_{HD\,140538}=}19.17\pm0.40\,\kmps$
}
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.
\textcolor{red}{
  Note that the uncertainty in $\mathrm{RV_{HD\,140538}}$ was computed
  by combining (in quadrature) the uncertainty ($0.4~\kmps$) in the
  heliocentric RV of the template star HD~74497 (G3V) and the
  uncertainty in the relative RV of HD~140538 ($0.02~\kmps$), measured
  by cross correlation with the template star.  Clearly, the former
  dominates in the uncertainty of
  $\mathrm{RV_{HD\,140538}}$ shown above. The uncertainty in the
  heliocentric RV of the template is rather large because it was
  determined from a few photospheric lines.
}

@@

\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
  observed (relative) RV values with a constant (a horizontal
  line). The constant used in the fit is determined from the weighted mean of
  the two RV measurements for each object.  The objects with
  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
  which appear in the right-most bin in the histogram. There
  are four objects which satisfy this condition. 
  \textcolor{red}{The expected distribution (dashed) for RV constant
  objects is also shown for a comparison, and is 
  normalized to the total number of objects that have $p>10^{-3}$}.
  The match between the expected distribution and the
  histogram is reasonable \textcolor{red}{(c.f.~Section~\ref{sub:Radial-velocities})},
  indicating that our uncertainty estimates 
  in RV values are also reasonable.  }

@@

Follow-up spectroscopic observations of the binary candidates
presented here are planned in near future. There are only a few RV
variable binary candidates identified in earlier surveys
(\citealt{guenther:2003}; \citealt{kenyon:2005}; \citealt{joergens:2006}).
As \citet{burgasser:2006} points out most of the current RV and
imaging surveys use samples from magnitude-limited survey, but one
should attempt to use the samples from volume-limited survey in order
to find a correct statistics on binary parameters more straightforwardly,
i.e. without correcting for bias. 
\textcolor{red}{
It is possible that our binary fraction is an overestimate since we
are biased to brighter objects. However the lack of a double-line
system suggests that a primary-to-secondary luminosity ratio of $\gg 1$
for the RV variables found in this paper. 
}
